Incentivizing Exploration by Heterogeneous Users

### 2018-10-01 Discussion.tex
proposed general proof

The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret}
incur exponential (in \ARMNUM) payment and regret in the initial
phases because the threshold $1/\log(s)$ required for incentivization
decreases slowly. 
This slow decrease is needed to bound the regret in the later phases
when the concentration inequality kicks in as in
Equation~(\ref{equ:small_regret_bound}).
In this section, we discuss two restrictions under which we can
modify the algorithm slightly and provide stronger bounds,
avoiding this exponential dependence.
Both problem settings are special cases of the more general
setting previously considered.

@@

When Assumption~\ref{a:discrete} holds,
we restrict the payment-eligibility criterion by only incentivizing
arms with much smaller probability to be pulled:
an arm $i$ is payment-eligible at time $t$ in phase $s$ when both of
the following are true:

\begin{itemize}
\item $i$ has been pulled at most $s$ times up to time $t$,
i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
the probability of pulling arm $i$ is less than $1/s$
(compared to $1/\log(s)$ in the general algorithm).
\end{itemize}

We refer to this modified version of
Algorithm~\ref{alg:basic-incentivizing} as the
\emph{Discrete-Preference Algorithm.}
We outline a proof of the following result for this algortithm under
Assumption~\ref{a:discrete} in Appendix~\ref{sec:discussion-proof1}.

\begin{theorem}
\label{rst:discrete}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm
has expected payment bounded above by 
$O \left(\ARMNUM^2/\MinProb \right)$
and expected regret bounded above by $O(\ARMNUM / \MinProb)$.
\end{theorem}

@@

When this assumption holds, we choose a different modification in the
definition of payment eligibility.
Let $s_0 = \exp(2/\MinProb)$.
An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both:
\begin{itemize}
\item $i$ has been pulled at most
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
\end{itemize}

This knowledge of \MinProb allows the algorithm to incentivize
significantly fewer arm pulls.
We refer to this modified version of
Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb
Algorithm.}
We outline a proof of the following result for this algortithm under
Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.

\begin{theorem}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has
expected payment  bounded above by  
$O(\ARMNUM^2 \cdot \max(1,(\TieDensity/\MinProb)^{5/2}))$ 
and expected regret bounded above by
%\begin{align*}
$O \left( \frac{\ARMNUM^2}{\MinProb^2}
%  + \frac{\ARMNUM^2}{\hat{z}^2}+\frac{\ARMNUM}{\hat{z}^3}
  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$.
%  \end{align*}
\end{theorem}

>>>>

The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret}
incur exponential (in \ARMNUM) payment and regret in the initial
phases because the threshold $1/\log(s)$ required for incentivization
decreases slowly. 
This slow decrease is needed to bound the regret in the later phases
when the concentration inequality kicks in as in
Equation~(\ref{equ:small_regret_bound}).
\bccomment{In this secion, we first introduce a modified version of
\textit{payment-eligible} definition with general probability threshold, and analyze
its regret and payment bound. Then we discuss two restrictions under
which we can provide stronger bounds, avoiding this exponential dependence.}
%In this section, we discuss two restrictions under which we can
%modify the algorithm slightly and provide stronger bounds,
%avoiding this exponential dependence.
Both problem settings are special cases of the more general
setting previously considered.

\bccomment{
\subsubsection{General Algorithm}
In this section, we introduce a more general definition of payment-eligible.
More specifically, an arm $i$ is payment-eligible at time $t$ in phase $s$ when both of
the following are true:

\begin{itemize}
\item $i$ has been pulled at most $s$ times up to time $t$,
i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
    the probability of pulling arm $i$ is less than $\phi(s)$
\end{itemize}

The general algorithm operates the same as Algorithm~\ref{alg:basic-incentivizing},
except using the new definition of payment-eligible.

With this definition of payment-eligible arms and probability threshold $\phi(s)$, we can
prove

\begin{theorem}
\label{rst:general}
With the probability threshold $\phi(s)$, the expected total payment for 
Algorithm~\ref{alg:basic-incentivizing} is at most XXX, and the expected
cumulative regret up to time T is bounded above by XXX.
\end{theorem}
}

@@

When Assumption~\ref{a:discrete} holds,
we restrict the payment-eligibility criterion by only incentivizing
arms with much smaller probability to be pulled:
\bccomment{we choose $\phi(s)=1/s$ (compared to $1/log(s)$ in Algorithm~\ref{alg:basic-incentivizing})}.

%an arm $i$ is payment-eligible at time $t$ in phase $s$ when both of
%the following are true:

%\begin{itemize}
%\item $i$ has been pulled at most $s$ times up to time $t$,
%i.e., $\NumPull{t}{i} \leq s$.
%\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
%the probability of pulling arm $i$ is less than $1/s$
%(compared to $1/\log(s)$ in the general algorithm).
%\end{itemize}

We refer to this modified version of
Algorithm~\ref{alg:basic-incentivizing} as the
\emph{Discrete-Preference Algorithm.}
\bccomment{
    Plug $\phi(s)=1/s$ into Theorem~\ref{rst:general}, after some calculation (see details in XXX), we get:
%We outline a proof of the following result for this algorithm under
%Assumption~\ref{a:discrete} in Appendix~\ref{sec:discussion-proof1}.

\begin{corollary}
\label{rst:discrete}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm
has expected payment bounded above by 
$O \left(\ARMNUM^2/\MinProb \right)$
and expected regret bounded above by $O(\ARMNUM / \MinProb)$.
\end{corollary}
}

%\begin{theorem}
%\label{rst:discrete}
%Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm
%has expected payment bounded above by 
%$O \left(\ARMNUM^2/\MinProb \right)$
%and expected regret bounded above by $O(\ARMNUM / \MinProb)$.
%\end{theorem}

@@

When this assumption holds, we choose a different modification in the
definition of payment eligibility.
Let $s_0 = \exp(2/\MinProb)$ \bccomment{ and we set $\phi(s)=1/\log(s+s_0)$.}

%An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
%if both:
%\begin{itemize}
%\item $i$ has been pulled at most
%$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
%\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
%the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
%\end{itemize}

This knowledge of \MinProb allows the algorithm to incentivize
significantly fewer arm pulls.
We refer to this modified version of
Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb
Algorithm.}

\bccomment{
Plug $\phi(s)=1/s$ into Theorem~\ref{rst:general}, after some calculation (see details in XXX), we get:
\begin{corollary}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has
expected payment  bounded above by  
$O(\ARMNUM^2 \cdot \max(1,(\TieDensity/\MinProb)^{5/2}))$ 
and expected regret bounded above by
\begin{align*}
O \left( \frac{\ARMNUM^2}{\MinProb^2}
  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right).
\end{align*}
\end{corollary}
}

%We outline a proof of the following result for this algorithm under
%Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.

%\begin{theorem}
%\label{rst:known-p}
%Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has
%expected payment  bounded above by  
%$O(\ARMNUM^2 \cdot \max(1,(\TieDensity/\MinProb)^{5/2}))$ 
%and expected regret bounded above by
%\begin{align*}
%$O \left( \frac{\ARMNUM^2}{\MinProb^2}
%  + \frac{\ARMNUM^2}{\hat{z}^2}+\frac{\ARMNUM}{\hat{z}^3}
%  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$.
%  \end{align*}
%\end{theorem}
